Lawvere-Tierney Sheafification\\ in Homotopy Type Theory

### 2016-01-19 paper/paper_acm.tex
pass on section 2

Another technical difficulty is the fact that sheafification in topos
theory uses the property that epimorphisms are coequalizers of their
kernel pairs. This property does not hold anymore in higher topoï, but
using Giraud-Rezk-Lurie axioms of $\infty$-topoï, the same property
holds by replacing kernel pairs by \v{C}ech nerves in the statement.

>>>>

Another technical difficulty is the fact that sheafification in topos
theory uses the property that epimorphisms are coequalizers of their
kernel pairs. This property does not hold anymore in higher topoï, but
using Giraud-Rezk-Lurie axioms of $\infty$-topoï, the same property
holds by replacing kernel pairs by \v{C}ech nerves in the statement
(Section~\ref{ssec:giraud-ax} presents the analogue theorem in
homotopy type theory).
